%%%%%%%%%%%%%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2020-07-24 09:05:07Z $
% $Pfad: GDV/Vortraege/latex - Ausarbeitung/Kapitel/Einleitung.tex $
% $Version: 4732 $
%
%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Connected Infrastructure Components}

\section{Infrastructure Integration}

\begin{itemize}
	\item \textbf{SimplyTag API Backend:} Serves as the primary source for log data. It collects and provides detailed information about HTTP requests, including trace IDs and status codes, for analysis.
	\item \textbf{Orgadata’s Logikal System:}Acts as the operational backbone for data-driven decision-making. This system contextualizes log data by linking it with construction-related project details, enabling precise threat detection.
	\item \textbf{External Threat Detection Tools:} To enhance the analytics, integration with external tools such as SIEM platforms or advanced machine learning models for threat prediction can be implemented. These tools offer additional layers of analysis and improve overall system resilience.
	\item \textbf{Cloud Infrastructure:} SimplyTag leverages cloud infrastructure to ensure scalability and reliability. The cloud platform supports large-scale log storage and computational power required for real-time analytics.
	\item \textbf{Mobile and Web Interfaces:} The analytics extend to user-facing interfaces like the SimplyTag mobile and web apps, ensuring seamless user interaction while maintaining robust security measures.
\end{itemize}

By connecting these components, the analytics create a comprehensive security ecosystem that is robust, scalable, and aligned with Orgadata’s operational goals.
  
  
  
   
  
   

 